### 2021-06-10 paper/model/testing.tex
Fix latex errors.

>>>>

\textcolor{red}{To Do für Appendix an der Stelle: Institutional details:}

\begin{itemize}
    \item \textcolor{red}{PCR tests only at doctor's office / test centers.}
    \item \textcolor{red}{Fraction PCR tests performed because of contact with infected
    people is small (quarantine mandate more common) -- need citation}
    \item \textcolor{red}{Rapid tests available in many pop up test centers,
    self-administered tests in every  drug store / supermarket, prices in early June < 1
    Euro}
\end{itemize}

### 2021-06-10 paper/report.tex
Add Fig 3d.
Fix latex errors.

Since early 2020, the CoViD-19 pandemic has presented an enormous challenge to humanity
on many dimensions. The development of highly effective vaccines holds the promise of
containment in the medium term. However, most countries find themselves many
months---and often years---away from reaching vaccination-induced herd immunity
\citep{Swaminathan2021}.\comment[id=K]{WHO Press Conference saying we won't reach herd
immunity in 2021}\comment[id=HM]{If we find a paper (s)he cites, would be even better}
In the meantime, it is of utmost importance to employ an effective mix of strategies for
containing the virus. The most frequent initial response was a set of non-pharmaceutical
interventions (NPIs) to reduce contacts between individuals. While this has allowed some
countries to sustain equilibria with very low infection numbers\footnote{See
    \citet{Contreras2021} for a theoretical equilibrium at low case numbers which is
    sustained with test-trace-and-isolate policies.}, most have seen large fluctuations of
infection rates. Containment measures have become increasingly diverse and now include
testing, more nuanced NPIs, and contact tracing. Neither these policies' effect nor the
influence of seasonal patterns or more infectious virus strains are well understood in
quantitative terms. This paper develops a model incorporating all these factors. The
framework allows to combine a wide variety of data in a timely fashion, making it useful
to predict the effects of various interventions. We apply the model to Germany and show
that rapid testing had the largest impact on the reduction in infections by almost 80\%
during the month of May 2021. We conclude that rapid tests have a large role to play at
least as long as vaccinations have not been offered to an entire population.

@@

    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=0.9 \textwidth]{../figures/results/figures/scenario_comparisons/school_scenarios/full_newly_infected}
        \caption{{Effects of different schooling scenarios after Easter}}
        \label{fig:schooling_scenarios_easter}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        % \includegraphics[width=0.9
        % \textwidth]{../figures/results/figures/scenario_comparisons/}
        \caption{{Effects of different work scenarios after Easter}}
        \label{fig:to_be_determined}
    \end{subfigure}
    \vskip3ex

>>>>

Since early 2020, the CoViD-19 pandemic has presented an enormous challenge to humanity
on many dimensions. The development of highly effective vaccines holds the promise of
containment in the medium term. However, most countries find themselves many
months---and often years---away from reaching vaccination-induced herd immunity
\citep{Swaminathan2021}.\comment[id=K]{WHO Press Conference saying we won't reach herd
immunity in 2021. She cites no source.}\comment[id=HM]{If we find a paper (s)he cites, would be even better}
In the meantime, it is of utmost importance to employ an effective mix of strategies for
containing the virus. The most frequent initial response was a set of non-pharmaceutical
interventions (NPIs) to reduce contacts between individuals. While this has allowed some
countries to sustain equilibria with very low infection numbers\footnote{See
    \citet{Contreras2021} for a theoretical equilibrium at low case numbers which is
    sustained with test-trace-and-isolate policies.}, most have seen large fluctuations of
infection rates. Containment measures have become increasingly diverse and now include
testing, more nuanced NPIs, and contact tracing. Neither these policies' effect nor the
influence of seasonal patterns or more infectious virus strains are well understood in
quantitative terms. This paper develops a model incorporating all these factors. The
framework allows to combine a wide variety of data in a timely fashion, making it useful
to predict the effects of various interventions. We apply the model to Germany and show
that rapid testing had the largest impact on the reduction in infections by almost 80\%
during the month of May 2021. We conclude that rapid tests have a large role to play at
least as long as vaccinations have not been offered to an entire population.

@@

    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=0.9 \textwidth]{../figures/results/figures/scenario_comparisons/school_scenarios/full_newly_infected}
        \caption{{Effects of different schooling scenarios after Easter}}
        \label{fig:schooling_scenarios_easter}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=0.9 \textwidth]{../figures/results/figures/scenario_comparisons/new_work_scenarios/full_newly_infected}
        \caption{{Effects of different work scenarios after Easter}}
        \label{fig:to_be_determined}
    \end{subfigure}
    \vskip3ex
